%\title{My two column CV}
%
% tccv (two columns curriculum vitae) is a LaTeX class inspired by
% the template found at latextemplates.com by Alessandro Plasmati.
%
% Create by Nicola Fontana, the original files can be downloaded from:
% http://dev.entidi.com/p/tccv/
%
\documentclass{tccv}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{hyperref}
\definecolor{light-gray}{gray}{0.9}
\begin{document}

\part{Christopher Asakawa}

\section{Work Objective}
Fresh Graduate with 2 years experience in developing with leading edge technologies, and with a willingness to learn new programming languages and procedures. 


\section{Education}

\begin{yearlist}

\item[Bachelors of Science]{2014 -- 2016}
     {Computer Science}
     {Portland State University}

\item{2009 -- 2014}
     {Associates in Liberal Arts}
     {Portland Community College}

\item{2003 -- 2007}
     {High School Diploma}
     {Aloha High School}
     
\end{yearlist}


\section{Work experience}

\begin{eventlist}

\item{July 2015 -- December 2015}
     {SalesForce}
     {Software Developer Intern}
     
Worked in a scrum team developing web applications. My primary task was to help with front end development, however I was also tasked with creating an maintaining automated end to end tests.

{\color{light-gray} \noindent\rule{8.7cm}{0.1pt} }
\item{December 2013 -- April 2015}
     {Papa Johns Pizza}
     {Delivery Driver}
     
Delivery Driver, and trained new hires.

{\color{light-gray} \noindent\rule{8.7cm}{0.1pt} }
\item{December 2009 -- April 2013}
     {The Springs}
     {Line Cook}

I had many job position transitions within this company. Including: server, bartender, prep cook and line cook.

{\color{light-gray} \noindent\rule{8.7cm}{0.1pt} }
\item{December 2008 -- December 2009}
     {Papa John's Pizza}
     {Manager}
     
I managed team members, inventory, food order, store cash, handled customer complaints and completed weekly reports.


\end{eventlist}


\section{References}
Available upon request.

\personal
    [asakawa.me]
    {1091 NW 208th Ter, Beaverton, OR}
    {(503) 724-7569}
    {chris@asakawa.me}

\section{Personal Projects}

\begin{yearlist}

\item{2016}
     {Fish Tank Random Number Generator}
     {I'm using a raspberry pi camera with openCV to track my fish. I translate their change of position into random values. This data is hosted on a server available for anyone to use.  }

\item{2016}
     {Fish Fate, Mobile Application}
     {Android and iOS application built with ionic. This application was built with the purpose of demonstrating the fish tank random number generator. It's features include: random dice roll, coin flip, magic 8-ball, lottery numbers, and more. }


\item{2014}
     {Electric Motorized Skateboard}
     {C programmed speed controller. Used physics, 3d drafing software, and basic electrical engineering to design the concept}




\end{yearlist}

\section{Freelance Web Development}
\href{http://fiveotree.com/}{FiveOTree.com}: e-commerce web site for a small clothing company based in Portland, OR. \\ \\
\href{http://talusdesign3d.com/}{talusdesign3d.com}: 
website for a Portland based 3D printing company. 

\section{Programming Knowledge}

\begin{factlist}

\item{Proficient}
     {Java, Python, C++, C, JavaScript, Angular, jQuery, HTML5, CSS3, bootstrap}

\item{Intermediate}
     {SQL, node.js, JSON, git, \LaTeX }

\item{Moderate}
     {PHP, XML, Ruby, iOS, Android}

\end{factlist}


\section{Relative Courses}

\begin{tabular}{ l  l }
- Data Structures  	    & - Network Security   \\
- Computer Systems		& - Computer Vision \\
- Discrete Structures  & - Open Source \\
- Computational Theory & - Databases \\
- Operating Systems    & - Calculus I, II, \& III \\
- Compilers 			& - Linear Algebra	 \\
- Software Engineering & - Statistics \\
- Computer Hardware	   &  - Public Speaking\\
- Algorithms			& - Technical Writing \\
\end{tabular}




\end{document}
